\documentclass[12pt]{extarticle}

\usepackage{enumitem}
\usepackage[cm]{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

\author{James T. Martin}

\begin{document}
%\section{\href{https://jamestmartin.me}{James T. Martin}, Software Developer}
\section{James T. Martin, Software Developer}
\begin{description}[noitemsep,labelwidth=2cm]
\item[Email] \href{mailto:James\%20Martin<james@jtmar.me>}{james@jtmar.me}
\item[Discord] jamestmartin\#7117
\item[Phone] \href{tel:+1-206-331-1994}{(206) 331-1994} (please text first so I know you're not spam)
\item[GitHub] \href{https://github.com/jamestmartin}{jamestmartin}
\item[Location] Renton, WA
\end{description}

\subsection{Experience}
\subsubsection{\href{https://dad.gallery}{Do Art Daily}, volunteer Ruby on Rails developer \hfill 2020}
\begin{itemize}
\item Discovered and fixed multiple severe security bugs by creating an automated test suite.
%\item Fixed those bugs: site-wide code injection, change anyone's password, personal information leak.
\item Designed and implemented secure cross-site authentication API and HAL+JSON REST API.
\end{itemize}

% Including the dates in the subsubsection title like this isn't necessarily semantic.
% I ought to come up with a better way.
\subsubsection{\href{https://proglangdesign.net}{Programming Language Design Community}, Administrator \& web developer \hfill 2018–2020}
\begin{itemize}
\item Led redesign of the website; used Jekyll to automate the generation of the community projects list.
\item Co-founded the Discord sub-community; moderated it and \href{https://reddit.com/r/ProgrammingLanguages}{/r/ProgrammingLanguages}.
\item Bridged the Discord and Freenode sub-communities via Matrix.
\end{itemize}

\subsubsection{Hazen Robotics Club, Java developer \hfill 2017–2019}
\begin{itemize}
\item Mentored programming at the district summer robotics camp for 90 hours.
\item Taught club members how to use Java and Git.
\item Collaborated to build robot controller programs for FIRST competitions.
\end{itemize}

{\tiny Childhood experience (2009–2016) omitted for relevence.}

\subsection{Skills}
\begin{itemize}
\item Languages: Java 8+, Rust, GHC Haskell, Agda, HTML5/XHTML, TypeScript
\item Tools: Git, GitHub, formal verification, continuous integration, bug tracking, unit testing
\item Administration: Debian GNU/Linux, Nginx, TLS deployment (incl. DNS CAA, HSTS, Let's Encrypt)
\end{itemize}


\subsection{Education}
\subsubsection{Hazen High School \hfill 2015–2019}
\begin{itemize}
\item Got high (4-5/5) scores on 7 AP exams, including Computer Science (5) and Calculus AB (4).
\item Learned shop skills (woodworking, welding) and received OSHA 10 certification.
\item Member of marching, symphonic, and jazz bands; received Sousa award in 2019.
\end{itemize}
\end{document}
