\documentclass[12pt]{extarticle}

\usepackage{enumitem}
\usepackage[cm]{fullpage}
\usepackage[utf8]{inputenc}
\usepackage{hyperref}

\DeclareUnicodeCharacter{2194}{\leftrightarrow}

\renewcommand{\familydefault}{\sfdefault}
\pagenumbering{gobble}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}

\author{James T. Martin}

\begin{document}
\section{\href{https://jamestmartin.me}{James T. Martin}, Web Developer}
\begin{description}[noitemsep,labelwidth=2cm]
\item[Email] \href{mailto:James\%20Martin<james@jtmar.me>}{james@jtmar.me}
\item[Phone] \href{tel:+1-206-331-1994}{(206) 331-1994}
\item[Location] Renton, WA
\item[GitHub] \href{https://github.com/jamestmartin}{jamestmartin}
\item[LinkedIn] \href{https://www.linkedin.com/in/jamestmartinme/}{jamestmartinme}
\end{description}

\subsection{Experience}
% Including the dates in the subsubsection title like this isn't necessarily semantic.
% I ought to come up with a better way.
\subsubsection{\href{https://proglangdesign.net}{Programming Language Design Community} \hfill June 2018 onward}
\begin{itemize}
\item Led redesign of \href{https://proglangdesign.net}{the website}.
\item Automated the generation of \href{https://proglangdesign.net/#projects}{the community projects list} using Jekyll.
\item \href{https://github.com/proglangdesign/matrix.proglangdesign.net}{Bridged} the \href{https://discord.gg/4Kjt3ZE}{Discord} and \href{https://irc.lc/freenode/proglangdesign}{Freenode} sub-communities via Matrix.
\item Co-founded the Discord sub-community; moderated it and \href{https://reddit.com/r/ProgrammingLanguages}{/r/ProgrammingLanguages}
\end{itemize}

\subsubsection{Hazen Robotics Club}
\begin{itemize}
\item Mentored programming at the summer robotics camp for 90 hours.
\item Taught club members to use Java and Git.
\item Collaborated to build robot controller programs for FIRST competitions.
\end{itemize}

\subsection{Skills}
\begin{itemize}
\item Languages: HTML5/XHTML, TypeScript, JavaScript, Java 8, Haskell, Agda
\item Tools: Git, GitHub, continuous integration, bug tracking, unit testing, formal verification
\item Administration: Debian GNU/Linux. Nginx
\item APIs: REST, JSON, JSON Schema, JSON-LD, HATEOAS
\item Security:
  \begin{itemize}
  \item TLS: Let's Encrypt, SSL Labs, DNS CAA, HSTS deployment
  \item Web: XSS prevention, CSRF prevention, CSP, input validation, SQL injection prevention
  \end{itemize}
\end{itemize}

\subsection{Education}
\subsubsection{\href{https://www.rentonschools.us/hazen}{Hazen High School} \hfill 2015 to 2019}
\begin{itemize}
\item Member of marching, symphonic, and jazz bands; recieved Sousa award in 2019.
\item Got high (4+) scores on 7 AP exams, including Computer Science (5) and Calculus AB (4).
\item Learned shop skills and recieved OSHA 10 certification.
\end{itemize}
\end{document}
